Creating the ``r params$package_name`` R package

### 2025-10-07 create-FSHybridPLS.Rmd
function normalize tested

```{r}
#' 
#' @export
curve_normalize <- function(functional, mean_functional, deno){
  # operation also takes care of the original_X

  functional_normalized <- fd(coef =
                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
                              basisobj = functional$basis
                              )#numerator
  functional_normalized <- times.fd(1/deno, functional_normalized)
  return(functional_normalized)
}
```

>>>>

```{r}
#' Normalize Functional Predictors in Hybrid Objects (Train/Test Split)
#'
#' Normalizes the functional components of both the training and testing 
#' `predictor_hybrid` objects using the mean and standard deviation derived
#' ONLY from the training data. The scalar components (Z) are left unchanged.
#'
#' @param train A `predictor_hybrid` object representing the training set.
#' @param test A `predictor_hybrid` object representing the testing set.
#' @return A list containing:
#'   \item{train}{The normalized training `predictor_hybrid` object.}
#'   \item{test}{The normalized testing `predictor_hybrid` object.}
#'   \item{deno_train}{A numeric vector of scaling factors used for each functional predictor.}
#' @export
curve_normalize_train_test <- function(train, test) {
  # --- Type Checks ---
  stopifnot(
    "'train' must be of class 'predictor_hybrid'" = inherits(train, "predictor_hybrid"),
    "'test' must be of class 'predictor_hybrid'" = inherits(test, "predictor_hybrid"),
    "Mismatch in number of functional predictors" = train$n_functional == test$n_functional
  )

  train_normalized <- train
  test_normalized <- test
  deno_train <- numeric(train$n_functional)

  # Iterate through each functional predictor (k)
  for (k in seq_len(train$n_functional)) {

    # 1. Determine centering and scaling factors from the TRAINING data only
    train_fd <- train$functional_list[[k]]

    # Calculate the mean function for centering
    mean_train <- fda::mean.fd(train_fd)

    # Calculate the standard deviation function
    sd_train <- fda::sd.fd(train_fd)

    # Calculate the scaling factor (L2 norm of the standard deviation function)
    deno_train[k] <- sqrt(fda::inprod(sd_train, sd_train))

    # Ensure scaling factor is positive
    if (deno_train[k] <= 1e-10) {
      warning(paste("Scaling factor for functional predictor", k, "is near zero. Skipping normalization for this predictor."))
      deno_train[k] <- 1 # Set to 1 to prevent division by zero, effectively no normalization
    }

    # 2. Normalize the TRAINING set
    train_normalized$functional_list[[k]] <- curve_normalize(
      train_fd, # Use original train data
      mean_train,
      deno_train[k]
    )

    # 3. Normalize the TEST set (using train factors to prevent leakage)
    test_normalized$functional_list[[k]] <-
      curve_normalize(
        test$functional_list[[k]], # Use original test data
        mean_train, # Centered by training mean
        deno_train[k] # Scaled by training SD
      )
  }

  # Return the modified hybrid objects and the scaling factors
  return( list(
    train = train_normalized,
    test = test_normalized,
    deno_train = deno_train
  ))
}
